Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-29 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Dividing into subsections...

@@

@@

Intuitively, the expectation value of an observable with respect to
an IVPM should be the minimum and maximum expectation value of the
same observable with respect to its consistent states. We found this
is true when we require our IVPM to be convex, and on a commuting
sub-event space, whose definition is given as follow.

@@

\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
decomposition~(\ref{eq:spectrum-decomposition}). A sub-event space~$\events'\subseteq\events$
is called a sub-event space induced by $\mathbf{O}$ if $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.

\end{definition}

@@

\begin{proof}Since $\events'$ is induced by $\mathbf{O}$, it is
commuting. By theorem~\ref{thm:sub-event-space}, there is set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$, and a convex classical
interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that 
\begin{equation}
\bar{\mu}=\bar{\mu}'\circ\tau\textrm{ .}\label{eq:sub-event-space}
\end{equation}
Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$ and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$
are the left-end and the right-end of $\bar{\mu}'$, respectively,
i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathscr{I}$
defined by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$.
Then, 
\begin{eqnarray*}
 &  & \expval{\mathbf{O}}_{\bar{\mu}}\\
 & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
 & \stackrel{\textrm{Equation }(\ref{eq:sub-event-space})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
 & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'\\
 & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
 & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\right]\\
 & \stackrel{\textrm{Claim }\ref{claim:min-max-core}}{=} & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\right]\\
 & \stackrel{\textrm{Definition }\ref{def:consistent-state}}{=} & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\right]\\
 & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ ,}
\end{eqnarray*}
where claim~\ref{claim:min-max-core} is going to be proved in the
next paragraph.

>>>>

\subsection{Expectation Values for Classical IVPMs}

@@

\subsection{Expectation Values for Quantum IVPMs}

@@

\subsection{Between Expectation Values for Classical and Quantum IVPMs}

Since the similarity between classical and quantum expectation values,
we would prove some lemmas\footnote{\yutsung{functor?}} which can
help us move the classical results to quantum.

\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
decomposition~(\ref{eq:spectrum-decomposition}). A sub-event space~$\events'\subseteq\events$
is called a sub-event space induced by $\mathbf{O}$ if it is the
minimal sub-event space satisfying $\left\{ P_{i}^{-}\right\} _{i=1}^{N^{-}}\cup\left\{ P_{i}^{+}\right\} _{i=1}^{N^{+}}\subseteq\events'$.\end{definition}

Notice that a sub-event space induced by any observable commutes so
that we can find a set~$\Omega$, a function~$\tau:\events'\rightarrow2^{\Omega}$
to pull quantum real-valued or interval-valued probability measures
to classical ones by theorem~\ref{thm:sub-event-space}. Although
it is a powerful tool, it would be more powerful if we can pull an
observable to a random variable as well.

\begin{definition}Given an observable~$\mathbf{O}$ with its spectral
decomposition~(\ref{eq:spectrum-decomposition}) and its inducing
sub-event space $\events'$, set~$\Omega$, and function~$\tau:\events'\rightarrow2^{\Omega}$.
Then, the random variable~$X:\Omega\rightarrow\mathbb{R}$ defined
by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$
is called the random variable induced by $\mathbf{O}$.\end{definition}

\begin{lemma}Adopting the definitions in this subsection. Given a
density matrix~$\rho$, there is a classical real-valued probability
measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$ such that $\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$.
Then, we have $\expval{\mathbf{O}}_{\rho}=\int X\rmd\mu'$.\end{lemma}

\begin{proof}
\begin{eqnarray*}
\expval{\mathbf{O}}_{\rho} & \stackrel{\textrm{Equation }(\ref{eq:quantum-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\\
 & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\\
 & \stackrel{\textrm{Equation }(\ref{eq:expectation})}{=} & \int X\rmd\left(\mu'\right)
\end{eqnarray*}
\end{proof}

\begin{lemma}Adopting the definitions in this subsection. Given a
quantum IVPM~$\bar{\mu}$, there is a classical real-valued probability
measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$ such that
$\bar{\mu}=\bar{\mu}'\circ\tau$. Then, we have $\expval{\mathbf{O}}_{\bar{\mu}}=\int X\rmd\bar{\mu}'$.\end{lemma}

\begin{proof}
\begin{eqnarray*}
\expval{\mathbf{O}}_{\bar{\mu}} & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
 & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
 & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'
\end{eqnarray*}
\end{proof}

\subsection{Between Expectation Values for Quantum Real-valued and Interval-valued
Probability Measures}

Intuitively, the expectation value of an observable with respect to
an IVPM should be the minimum and maximum expectation value of the
same observable with respect to its consistent states. We found this
is true when we require our IVPM to be convex, and on a commuting
sub-event space, whose definition is given in the next subsection.

@@

@@

\begin{proof}Since $\events'$ is induced by $\mathbf{O}$, it is
commuting. By theorem~\ref{thm:sub-event-space}, there is set~$\Omega$,
a function~$\tau:\events'\rightarrow2^{\Omega}$, and a convex classical
interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that 
\begin{equation}
\bar{\mu}=\bar{\mu}'\circ\tau\textrm{ .}\label{eq:sub-event-space}
\end{equation}
Let $\mul[\prime]:\events'\rightarrow\left[0,1\right]$ and $\mur[\prime]:\events'\rightarrow\left[0,1\right]$
are the left-end and the right-end of $\bar{\mu}'$, respectively,
i.e., $\bar{\mu}'\left(E\right)=\left[\mul[\prime]\left(E\right),\mur[\prime]\left(E\right)\right]$
for all $E\in2^{\Omega}$. Consider the random variable~$X:\Omega\rightarrow\mathbb{R}$
defined by $X=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mathbf{1}_{\tau\left(P_{i}^{s}\right)}$.
Then, 
\begin{eqnarray*}
 &  & \expval{\mathbf{O}}_{\bar{\mu}}\\
 & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\\
 & \stackrel{\textrm{Equation }(\ref{eq:sub-event-space})}{=} & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right),\Delta\mur[\prime]\left(\tau\left(P_{i}^{s\prime}\right)\right)\right]\\
 & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \int X\rmd\bar{\mu}'\\
 & \stackrel{\textrm{Theorem }\ref{thm:Rosenmuller}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu',\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\int X\rmd\mu'\right]\\
 & \stackrel{\textrm{Definition }\ref{def:Choquet}}{=} & \left[\min_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right),\max_{\mu'\in\mathrm{core}\left(\bar{\mu}'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu'\left(\tau\left(P_{i}^{s}\right)\right)\right]\\
 & \stackrel{\textrm{Claim }\ref{claim:min-max-core}}{=} & \left[\min_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right),\max_{\mu\in\mathrm{core}\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu\left(P_{i}^{s}\right)\right]\\
 & \stackrel{\textrm{Definition }\ref{def:consistent-state}}{=} & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right),\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\mu_{\rho}^{\mathrm{B}}\left(P_{i}^{s}\right)\right]\\
 & \stackrel{\textrm{Equation }(\ref{eq:quantum-interval-expectation})}{=} & \left[\min_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho},\max_{\rho\in\coreBorn\left(\bar{\mu},\events'\right)}\expval{\mathbf{O}}_{\rho}\right]\textrm{ ,}
\end{eqnarray*}
where claim~\ref{claim:min-max-core} is going to be proved in the
next paragraph.
